Sparsely Activated Networks

### 2023-05-11 latex/ms.tex
.

\begin{figure*}[!t]
	\centering
	\subfloat{\includegraphics[width=0.2\textwidth]{python/bin/UCI-epilepsy-identity-1d-2-activations-0.pdf}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/bin/UCI-epilepsy-relu-1d-2-activations-0.pdf}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/bin/UCI-epilepsy-top-k-absolutes-1d-2-activations-0.pdf}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/bin/UCI-epilepsy-extrema-pool-indices-1d-2-activations-0.pdf}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/bin/UCI-epilepsy-extrema-1d-2-activations-0.pdf}}
	\\
	\setcounter{subfigure}{0}
	\subfloat[Identity]{\includegraphics[width=0.2\textwidth]{python/bin/MNIST-identity-2d-2-activations-1.pdf}\label{subfig:identity}}
	\subfloat[ReLU]{\includegraphics[width=0.2\textwidth]{python/bin/MNIST-relu-2d-2-activations-0.pdf}\label{subfig:relu}}
	\subfloat[top-k absolutes]{\includegraphics[width=0.2\textwidth]{python/bin/MNIST-top-k-absolutes-2d-2-activations-0.pdf}\label{subfig:topkabsolutes}}
	\subfloat[Extrema-Pool indices]{\includegraphics[width=0.2\textwidth]{python/bin/MNIST-extrema-pool-indices-2d-2-activations-0.pdf}\label{subfig:extremapoolindices}}
	\subfloat[Extrema]{\includegraphics[width=0.2\textwidth]{python/bin/MNIST-extrema-2d-2-activations-0.pdf}\label{subfig:extrema}}
	\caption{Visualization of the activation maps of five activation functions (Identity, ReLU, top-k absolutes, Extrema-Pool indices and Extrema) for 1D and 2D input in the top and bottom row respectively.
	The 1D input to the activation functions is denoted with the continuous transparent green line using an example from the UCI dataset.
	The output of each activation function is denoted with the cyan stem lines with blue markers.
	The 2D example depicts only the output of the activation functions using an example from the MNIST dataset.
	}\label{fig:activationfunctions}
\end{figure*}

@@

\begin{algorithm}[H]
	\caption{Extrema detection with minimum extrema distance $med$}\label{alg:extrema}
	\begin{algorithmic}[1]
		\renewcommand{\algorithmicrequire}{\textbf{Input:}}
		\renewcommand{\algorithmicensure}{\textbf{Output:}}
		\REQUIRE{$s$, $med$}
		\ENSURE{$\alpha$}
		\STATE{$peaks \leftarrow \left(\frac{d s}{d t}^+ \geq 0\right) \land \left(\frac{d s}{d t}^- < 0\right)$}
		\STATE{$valleys \leftarrow \left(\frac{d s}{d t}^+ < 0\right) \land \left(\frac{d s}{d t}^- \geq 0\right)$}
		\\\textit{\scriptsize \# + and - denote one sample padding to the right and left respectively}
		\STATE{$z \leftarrow peaks \lor valleys$}
		\STATE{$e \leftarrow z > 0$}
		\STATE{$e_{ind} \leftarrow sort(z)$}
		\STATE{$e_{sorted} \leftarrow e(e_{ind})$}
		\STATE{$e_{seco}(i) \leftarrow 0, i=1\ldots card(s)$}
		\\\textit{\scriptsize \# $e_{seco}$ denotes a boolean vector for the secondary extrema indices}
		\FOR{$i$ = 0 to $card(s)$}
		\IF{$\lnot e_{seco}(i)$}
		\STATE{$e_r \leftarrow e \geq e_{ind}(i) - med$}
		\STATE{$e_l \leftarrow e \leq e_{ind}(i) + med$}
		\STATE{$e_m \leftarrow e_r \land e_l$}
		\STATE{$e_{seco} \leftarrow e_{seco} \lor e_m$}
		\STATE{$e_{seco}(i) \leftarrow 0$}
		\ENDIF{}
		\ENDFOR{}
		\STATE{$\alpha_{ind} \leftarrow e_{sorted}(\lnot e_{seco})$}
		\\\textit{\scriptsize \# $\alpha_{ind}$ denotes the indices of $\alpha$ with non-zero value}
		\STATE{$\alpha(i) \leftarrow 0, i=1\ldots card(s)$}
		\FOR{$i$ = 0 to $card(s)$}
		\STATE{$\alpha(\alpha_{ind}(i)) \leftarrow s(\alpha_{ind}(i))$}
		\ENDFOR{}
		\RETURN{$\alpha$}
	\end{algorithmic}
\end{algorithm}

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-signal.pdf}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-reconstructed.pdf}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-reconstruction-0.pdf}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-activations-0.pdf}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-similarity-0.pdf}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/UCI-epilepsy-extrema-1d-2-kernel-0.pdf}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-signal.pdf}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-reconstructed.pdf}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-reconstruction-0.pdf}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-activations-0.pdf}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-similarity-0.pdf}};
			\node[opacity=0, left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/UCI-epilepsy-extrema-1d-2-kernel-0.pdf}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-reconstruction-1.pdf}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-activations-1.pdf}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-similarity-1.pdf}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/UCI-epilepsy-extrema-1d-2-kernel-1.pdf}};

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-signal.pdf}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-reconstructed.pdf}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-reconstruction-0.pdf}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-activations-0.pdf}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-similarity-0.pdf}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/MNIST-extrema-2d-2-kernel-0.pdf}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-signal.pdf}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-reconstructed.pdf}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-reconstruction-0.pdf}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-activations-0.pdf}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-similarity-0.pdf}};
			\node[opacity=0, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/MNIST-extrema-2d-2-kernel-0.pdf}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-reconstruction-1.pdf}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-activations-1.pdf}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-similarity-1.pdf}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/MNIST-extrema-2d-2-kernel-1.pdf}};

@@

\begin{figure*}[!t]
	\includegraphics[width=0.245\textwidth]{python/bin/apnea-ecg.pdf}
	\includegraphics[width=0.245\textwidth]{python/bin/bidmc.pdf}
	\includegraphics[width=0.245\textwidth]{python/bin/bpssrat.pdf}
	\includegraphics[width=0.245\textwidth]{python/bin/cebsdb.pdf}
	\\
	\includegraphics[width=0.245\textwidth]{python/bin/ctu-uhb-ctgdb.pdf}
	\includegraphics[width=0.245\textwidth]{python/bin/drivedb.pdf}
	\includegraphics[width=0.245\textwidth]{python/bin/emgdb.pdf}
	\includegraphics[width=0.245\textwidth]{python/bin/mitdb.pdf}
	\\
	\includegraphics[width=0.245\textwidth]{python/bin/noneeg.pdf}
	\includegraphics[width=0.245\textwidth]{python/bin/prcp.pdf}
	\includegraphics[width=0.245\textwidth]{python/bin/shhpsgdb.pdf}
	\includegraphics[width=0.245\textwidth]{python/bin/slpdb.pdf}
	\\
	\includegraphics[width=0.245\textwidth]{python/bin/sufhsdb.pdf}
	\includegraphics[width=0.245\textwidth]{python/bin/voiced.pdf}
	\includegraphics[width=0.245\textwidth]{python/bin/wrist.pdf}
	\includegraphics[width=0.245\textwidth]{python/bin/legend.pdf}
	\caption{Inverse compression ratio ($CR^{-1}$) vs.\ normalized reconstruction loss ($\tilde{\mathcal{L}}$) for the $15$ datasets of Physionet for various kernel sizes.
	The five inner plots with the yellow background on the right of each subplot, depict the corresponding kernel for the kernel size that achieved the best $\bar\varphi$.}\label{fig:crrl}
\end{figure*}

\begin{figure*}[!t]
	\centering
	\subfloat[Density plot $CR^{-1}$ vs. $\tilde{\mathcal{L}}$]{\includegraphics[width=0.32\textwidth]{python/bin/crrl-density-plot.pdf}\label{subfig:crrl_density_plot}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $epochs$]{\includegraphics[width=0.32\textwidth]{python/bin/mean-flithos-validation-epochs.pdf}\label{subfig:flithos-epochs}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $m$]{\includegraphics[width=0.32\textwidth]{python/bin/mean-flithos-variable-kernel-size-list.pdf}\label{subfig:flithos_m}}
	\caption{Aggregated results of the evaluation of the Physionet databases using the $\bar\varphi$ metric.
	The density plot was created using kernel density estimation with Gaussian kernels and the confidence intervals denote one standard deviation.}\label{fig:flithos}
\end{figure*}

@@

	\includegraphics[width=0.06\textwidth]{python/bin/apnea-ecg-relu-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/bidmc-relu-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/bpssrat-relu-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/cebsdb-relu-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/ctu-uhb-ctgdb-relu-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/drivedb-relu-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/emgdb-relu-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/mitdb-relu-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/noneeg-relu-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/prcp-relu-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/shhpsgdb-relu-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/slpdb-relu-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/sufhsdb-relu-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/voiced-relu-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/wrist-relu-1d-1-kernel-0.pdf}

@@

	\includegraphics[width=0.06\textwidth]{python/bin/apnea-ecg-top-k-absolutes-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/bidmc-top-k-absolutes-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/bpssrat-top-k-absolutes-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/cebsdb-top-k-absolutes-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/ctu-uhb-ctgdb-top-k-absolutes-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/drivedb-top-k-absolutes-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/emgdb-top-k-absolutes-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/mitdb-top-k-absolutes-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/noneeg-top-k-absolutes-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/prcp-top-k-absolutes-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/shhpsgdb-top-k-absolutes-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/slpdb-top-k-absolutes-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/sufhsdb-top-k-absolutes-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/voiced-top-k-absolutes-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/wrist-top-k-absolutes-1d-1-kernel-0.pdf}

@@

	\includegraphics[width=0.06\textwidth]{python/bin/apnea-ecg-extrema-pool-indices-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/bidmc-extrema-pool-indices-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/bpssrat-extrema-pool-indices-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/cebsdb-extrema-pool-indices-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/ctu-uhb-ctgdb-extrema-pool-indices-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/drivedb-extrema-pool-indices-1d-1-kernel-0.pdf}
	\includegraphics[width=0.06\textwidth]{python/bin/emgdb-extrema-pool-indices-1d-1-kernel-0.pdf}

>>>>

\begin{figure*}[!t]
	\centering
	\subfloat{\includegraphics[width=0.2\textwidth]{python/bin/UCI-epilepsy-identity-1d-2-activations-0.png}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/bin/UCI-epilepsy-relu-1d-2-activations-0.png}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/bin/UCI-epilepsy-top-k-absolutes-1d-2-activations-0.png}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/bin/UCI-epilepsy-extrema-pool-indices-1d-2-activations-0.png}}
	\subfloat{\includegraphics[width=0.2\textwidth]{python/bin/UCI-epilepsy-extrema-1d-2-activations-0.png}}
	\\
	\setcounter{subfigure}{0}
	\subfloat[Identity]{\includegraphics[width=0.2\textwidth]{python/bin/MNIST-identity-2d-2-activations-1.png}\label{subfig:identity}}
	\subfloat[ReLU]{\includegraphics[width=0.2\textwidth]{python/bin/MNIST-relu-2d-2-activations-0.png}\label{subfig:relu}}
	\subfloat[top-k absolutes]{\includegraphics[width=0.2\textwidth]{python/bin/MNIST-top-k-absolutes-2d-2-activations-0.png}\label{subfig:topkabsolutes}}
	\subfloat[Extrema-Pool indices]{\includegraphics[width=0.2\textwidth]{python/bin/MNIST-extrema-pool-indices-2d-2-activations-0.png}\label{subfig:extremapoolindices}}
	\subfloat[Extrema]{\includegraphics[width=0.2\textwidth]{python/bin/MNIST-extrema-2d-2-activations-0.png}\label{subfig:extrema}}
	\caption{Visualization of the activation maps of five activation functions (Identity, ReLU, top-k absolutes, Extrema-Pool indices and Extrema) for 1D and 2D input in the top and bottom row respectively.
	The 1D input to the activation functions is denoted with the continuous transparent green line using an example from the UCI dataset.
	The output of each activation function is denoted with the cyan stem lines with blue markers.
	The 2D example depicts only the output of the activation functions using an example from the MNIST dataset.
	}\label{fig:activationfunctions}
\end{figure*}

@@

\begin{algorithm}[H]
	\caption{Extrema detection with minimum extrema distance $med$}\label{alg:extrema}
	\begin{algorithmic}[1]
		\renewcommand{\algorithmicrequire}{\textbf{Input:}}
		\renewcommand{\algorithmicensure}{\textbf{Output:}}
		\REQUIRE{$s$, $med$}
		\ENSURE{$\alpha$}
		\STATE{$peaks \leftarrow \left(\frac{d s}{d t}^+ \geq 0\right) \land \left(\frac{d s}{d t}^- < 0\right)$}
		\STATE{$valleys \leftarrow \left(\frac{d s}{d t}^+ < 0\right) \land \left(\frac{d s}{d t}^- \geq 0\right)$}
		\\\textit{\scriptsize \# + and - denote one sample padding to the right and left respectively} % chktex 8
		\STATE{$z \leftarrow peaks \lor valleys$}
		\STATE{$e \leftarrow z > 0$}
		\STATE{$e_{ind} \leftarrow sort(z)$}
		\STATE{$e_{sorted} \leftarrow e(e_{ind})$}
		\STATE{$e_{seco}(i) \leftarrow 0, i=1\ldots card(s)$}
		\\\textit{\scriptsize \# $e_{seco}$ denotes a boolean vector for the secondary extrema indices}
		\FOR{$i$ = 0 to $card(s)$}
		\IF{$\lnot e_{seco}(i)$}
		\STATE{$e_r \leftarrow e \geq e_{ind}(i) - med$}
		\STATE{$e_l \leftarrow e \leq e_{ind}(i) + med$}
		\STATE{$e_m \leftarrow e_r \land e_l$}
		\STATE{$e_{seco} \leftarrow e_{seco} \lor e_m$}
		\STATE{$e_{seco}(i) \leftarrow 0$}
		\ENDIF{}
		\ENDFOR{}
		\STATE{$\alpha_{ind} \leftarrow e_{sorted}(\lnot e_{seco})$}
		\\\textit{\scriptsize \# $\alpha_{ind}$ denotes the indices of $\alpha$ with non-zero value}
		\STATE{$\alpha(i) \leftarrow 0, i=1\ldots card(s)$}
		\FOR{$i$ = 0 to $card(s)$}
		\STATE{$\alpha(\alpha_{ind}(i)) \leftarrow s(\alpha_{ind}(i))$}
		\ENDFOR{}
		\RETURN{$\alpha$}
	\end{algorithmic}
\end{algorithm}

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-signal.png}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-reconstructed.png}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-reconstruction-0.png}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-activations-0.png}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-similarity-0.png}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/UCI-epilepsy-extrema-1d-2-kernel-0.png}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-signal.png}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-reconstructed.png}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-reconstruction-0.png}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-activations-0.png}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-similarity-0.png}};
			\node[opacity=0, left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/UCI-epilepsy-extrema-1d-2-kernel-0.png}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-reconstruction-1.png}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-activations-1.png}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/UCI-epilepsy-extrema-1d-2-similarity-1.png}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/UCI-epilepsy-extrema-1d-2-kernel-1.png}};

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-signal.png}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-reconstructed.png}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-reconstruction-0.png}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-activations-0.png}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-similarity-0.png}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/MNIST-extrema-2d-2-kernel-0.png}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-signal.png}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-reconstructed.png}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-reconstruction-0.png}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-activations-0.png}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-similarity-0.png}};
			\node[opacity=0, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/MNIST-extrema-2d-2-kernel-0.png}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-reconstruction-1.png}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-activations-1.png}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{python/bin/MNIST-extrema-2d-2-similarity-1.png}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{python/bin/MNIST-extrema-2d-2-kernel-1.png}};

@@

\begin{figure*}[!t]
	\includegraphics[width=0.245\textwidth]{python/bin/apnea-ecg.png}
	\includegraphics[width=0.245\textwidth]{python/bin/bidmc.png}
	\includegraphics[width=0.245\textwidth]{python/bin/bpssrat.png}
	\includegraphics[width=0.245\textwidth]{python/bin/cebsdb.png}
	\\
	\includegraphics[width=0.245\textwidth]{python/bin/ctu-uhb-ctgdb.png}
	\includegraphics[width=0.245\textwidth]{python/bin/drivedb.png}
	\includegraphics[width=0.245\textwidth]{python/bin/emgdb.png}
	\includegraphics[width=0.245\textwidth]{python/bin/mitdb.png}
	\\
	\includegraphics[width=0.245\textwidth]{python/bin/noneeg.png}
	\includegraphics[width=0.245\textwidth]{python/bin/prcp.png}
	\includegraphics[width=0.245\textwidth]{python/bin/shhpsgdb.png}
	\includegraphics[width=0.245\textwidth]{python/bin/slpdb.png}
	\\
	\includegraphics[width=0.245\textwidth]{python/bin/sufhsdb.png}
	\includegraphics[width=0.245\textwidth]{python/bin/voiced.png}
	\includegraphics[width=0.245\textwidth]{python/bin/wrist.png}
	\includegraphics[width=0.245\textwidth]{python/bin/legend.png}
	\caption{Inverse compression ratio ($CR^{-1}$) vs.\ normalized reconstruction loss ($\tilde{\mathcal{L}}$) for the $15$ datasets of Physionet for various kernel sizes.
	The five inner plots with the yellow background on the right of each subplot, depict the corresponding kernel for the kernel size that achieved the best $\bar\varphi$.}\label{fig:crrl}
\end{figure*}

\begin{figure*}[!t]
	\centering
	\subfloat[Density plot $CR^{-1}$ vs. $\tilde{\mathcal{L}}$]{\includegraphics[width=0.32\textwidth]{python/bin/crrl-density-plot.png}\label{subfig:crrl_density_plot}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $epochs$]{\includegraphics[width=0.32\textwidth]{python/bin/mean-flithos-validation-epochs.png}\label{subfig:flithos-epochs}}
	\subfloat[Confidence intervals $\bar\varphi$ vs. $m$]{\includegraphics[width=0.32\textwidth]{python/bin/mean-flithos-variable-kernel-size-list.png}\label{subfig:flithos_m}}
	\caption{Aggregated results of the evaluation of the Physionet databases using the $\bar\varphi$ metric.
	The density plot was created using kernel density estimation with Gaussian kernels and the confidence intervals denote one standard deviation.}\label{fig:flithos}
\end{figure*}

@@

	\includegraphics[width=0.06\textwidth]{python/bin/apnea-ecg-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/bidmc-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/bpssrat-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/cebsdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/ctu-uhb-ctgdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/drivedb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/emgdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/mitdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/noneeg-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/prcp-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/shhpsgdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/slpdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/sufhsdb-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/voiced-relu-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/wrist-relu-1d-1-kernel-0.png}

@@

	\includegraphics[width=0.06\textwidth]{python/bin/apnea-ecg-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/bidmc-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/bpssrat-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/cebsdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/ctu-uhb-ctgdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/drivedb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/emgdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/mitdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/noneeg-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/prcp-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/shhpsgdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/slpdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/sufhsdb-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/voiced-top-k-absolutes-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/wrist-top-k-absolutes-1d-1-kernel-0.png}

@@

	\includegraphics[width=0.06\textwidth]{python/bin/apnea-ecg-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/bidmc-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/bpssrat-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/cebsdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/ctu-uhb-ctgdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/drivedb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/emgdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/mitdb-extrema-pool-indices-1d-1-kernel-0.png}
	\includegraphics[width=0.06\textwidth]{python/bin/noneeg-extrema-pool-indices-1d-1-kernel-0.png}
